---
title: "BQL Data Analysis"
author: "Jackie Chin & Mia Forsline"
date: "2025-04-11"
output: html_document
---

# Objective

- To pull up the descriptives/demographic data for the Black, Queer & Liberated mental health intervention project. 
- To clean and visualize the data
- To run and interpret: 
  - non-parametric ANOVA tests (AKA Friedman's tests)
  - pairwise comparison tests

This is part of Jacquelyn Chin's 2025 dissertation defense. Almost at the finish line, baddie!!

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = FALSE,
	message = FALSE,
	warning = FALSE
)
options(knitr.duplicate.label = "allow",
        scipen = 999)

#install packages if necessary, then load libraries
if (!require(librarian)){
  install.packages("librarian")
  library(librarian)
}
librarian::shelf(
  here, #to build file paths
  janitor, #for column name cleaning
  lubridate, #for working with dates 
  readxl, #read in Excel files
  tidyverse, #general data cleaning functions and collection of common packages
  writexl #save Excel files
  )
```

# Read in the data
- The raw Excel data was exported from Qualtrics 

First, create an R chunk: Command + option + I makes a code chunk appear on the Mac

Note: you can run an entire R code chunk by pressing the green arrow button OR using Shift + Command + Return on a Mac 

```{r read_in_race}
#filepath & here function takes everything in green & helps R locate the correct file path
filepath <- here("../")
#"../" means one file outside of this file
print(filepath) #double check the filepath is correct
#filename function tells R where the exact file is located

filename <- list.files(path = filepath, pattern = "BQL Survey Data - CLEAN.xlsx") #which file do we want to read in?

print(filename) #check which file we have selected
#print function means 'show me what is in this file'

#read_excel() reads in Excel files
BQL_Data <- read_excel(path = here(filepath, filename[1]), sheet = 1) 
```

# Cleaning the data 
We want to drop the "dummy" participants from survey results 
- AKA we want to remove fake data based on Q1
- Jackie indicated that there are 3 real participants: BELL, BER, and LAS
- We will remove everyone else 

```{r}
#(option + minus sign) is the keyboard shortcut for the assignment arrow (<-)
##you can also type out the assignment arrow

#first, we will create a "clean" version of the data based on the original BQL_Data object
BQL_Data_Clean <- BQL_Data %>% 
  #(shift + command + m) creates a pipe symbol
  
  #then we will filter based on column Q1
  filter(
    Q1 == "BELL" | Q1 == "BER" | Q1 == "LAS"
  ) %>% 
  
  #then we will drop rows that have NA values in column Q4 because this row is incomplete data 
  drop_na(Q4)
#filter function tells Data what to pull out from the Excel sheet
```

# Descriptive/Demographic Data

Next, we want to count/tally up Descriptive numbers from pre-survey data

NUMBER (#) of people who checked each category
- Race/Ethnicity
- Gender
- Sexual Orientation
- Relationship Status
- Education
- Employment
- Income
- Political Action

First, we will look at all the questions participants answered (in the Pre-Survey)

```{r}
questions <- BQL_Data %>% 
  filter(StartDate == "Start Date") %>% 
  pivot_longer(
    cols = starts_with("Q"),
    names_to = "Question",
    values_to = "Description"
  ) %>% 
  select(
    Question,
    Description
  )

nrow(questions)
```

Then we will look at what participants answered when asked about: 
- their Race/Ethnicity (Q36 and Q36_11_TEXT)

```{r}
race_ethnicity <- BQL_Data_Clean %>% 
  select(Q1,
         Q36,
         Q36_11_TEXT)
```





PHQ-4 Anxiety & Depression (ALL ITEMS in Q8.Q8_1, Q8_2, Q8_3, and Q8_4)
- Averaging the total of this measure's items for 3 people
- Running the Friedman's Test Across Pre-Survey > Week 2 > Week 4 > Week 6 > Post-Test > Follow-Up 
- This will tell us the spread of the 3 values across 6 timepoints

