---
title: "BQL Data Analysis"
author: "Jackie Chin & Mia Forsline"
date: "2025-04-11"
output: html_document
---

# Objective

- To pull up the descriptives/demographic data for the Black, Queer & Liberated mental health intervention project. 
- To clean the data
- To summarize and visualize demographic data 

This is part of Jacquelyn Chin's 2025 dissertation defense. Almost at the finish line, baddie!!

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = FALSE,
	message = FALSE,
	warning = FALSE
)
options(knitr.duplicate.label = "allow",
        scipen = 999)

#install packages if necessary, then load libraries
if (!require(librarian)){
  install.packages("librarian")
  library(librarian)
}
librarian::shelf(
  #expss, #to make tables
  here, #to build file paths
  janitor, #for column name cleaning
  lubridate, #for working with dates 
  readxl, #read in Excel files
  stringr, #to clean data 
  tidyr, #data cleaning
  tidyverse, #general data cleaning functions and collection of common packages
  dplyr, #case_match
  writexl #save Excel files
  )
```

# Read in Survey Data
- The raw Excel data was exported from Qualtrics 

First, create an R chunk: Command + option + I makes a code chunk appear on the Mac

Note: you can run an entire R code chunk by pressing the green arrow button OR using Shift + Command + Return on a Mac 

```{r read_in_data}
#filepath & here function takes everything in green & helps R locate the correct file path
filepath <- here("../")
#"../" means one file outside of this file
print(filepath) #double check the filepath is correct
#filename function tells R where the exact file is located

filename <- list.files(path = filepath, pattern = "BQL Survey Data - CLEAN - FINAL.xlsx") #which file do we want to read in?

print(filename) #check which file we have selected
#print function means 'show me what is in this file'

#read_excel() reads in Excel files
pre_survey <- read_excel(path = here(filepath, filename[1]), sheet = 1) 
week1 <- read_excel(path = here(filepath, filename[1]), sheet = 2) 
week2 <- read_excel(path = here(filepath, filename[1]), sheet = 3)
week3 <- read_excel(path = here(filepath, filename[1]), sheet = 4)
week4 <- read_excel(path = here(filepath, filename[1]), sheet = 5)
week5 <- read_excel(path = here(filepath, filename[1]), sheet = 6)
week6 <- read_excel(path = here(filepath, filename[1]), sheet = 7)
post_survey <- read_excel(path = here(filepath, filename[1]), sheet = 8)
follow_up <- read_excel(path = here(filepath, filename[1]), sheet = 9)
```

# Clean the data 
We want to drop the "dummy" participants from pre-survey results 
- AKA we want to remove fake data based on Q1
- Jackie indicated that there are 3 real participants: BELL, BER, and LAS
- We will remove everyone else 

Week 1 had no real data

Refer to BQL Survey Data - CLEAN - FINAL to see how many real participants completed each week's survey

```{r}
#(option + minus sign) is the keyboard shortcut for the assignment arrow (<-)
##you can also type out the assignment arrow

#first, we will create a "clean" version of the data based on the original BQL_Data object
pre_survey_clean <- pre_survey %>% 
  #(shift + command + m) creates a pipe symbol
  
  #then we will filter based on column Q1
  filter(
    Q1 == "BELL" | Q1 == "BER" | Q1 == "LAS"
  ) %>% 
  
  #then we will drop rows that have NA values in column Q4 because this row is incomplete data 
  drop_na(Q4)
#filter function tells Data what to pull out from the Excel sheet

week2_clean <- week2 %>% 
  mutate(
    Q1 = toupper(Q1)
  ) %>% 
  filter(
    Q1 == "BELL" | Q1 == "LAS" | Q1 == "TOR"
  )

week3_clean <- week3 %>% 
  mutate(
    Q1 = toupper(Q1)
  ) %>% 
  filter(
    Q1 == "BAL" | Q1 == "LAS" | Q1 == "TOR"
  )

week4_clean <- week4 %>% 
  mutate(
    Q1 = toupper(Q1)
  ) %>% 
  filter(
    Q1 == "LAS" | Q1 == "TOR"
  )

week5_clean <- week5 %>% 
  mutate(
    Q1 = toupper(Q1)
  ) %>% 
  filter(
    Q1 == "LAS" | Q1 == "TOR"
  )

week6_clean <- week6 %>% 
  mutate(
    Q1 = toupper(Q1)
  ) %>% 
  filter(
    Q1 == "LAS"
  )

post_survey_clean <- post_survey %>% 
  mutate(
    Q1 = toupper(Q1)
  ) %>% 
  filter(
    Q1 == "LAS"
  )

follow_up_clean <- follow_up %>% 
  mutate(
    Q1 = toupper(Q1)
  ) %>% 
  filter(
    Q1 == "TOR"
  )
```

# Descriptive/Demographic Data

Next, we want to count/tally up Descriptive numbers from pre-survey data

NUMBER (#) of people who checked each category
- Race/Ethnicity
- Gender
- Sexual Orientation
- Relationship Status
- Education
- Employment
- Income
- Political Action

First, we will look at all the questions participants answered (in the Pre-Survey)

```{r questions}
questions <- pre_survey %>% 
  filter(StartDate == "Start Date") %>% 
  pivot_longer(
    cols = starts_with("Q"),
    names_to = "Question",
    values_to = "Description"
  ) %>% 
  select(
    Question,
    Description
  )

nrow(questions)
```

Next, we will read about how to [Recode Variables](https://www.anyamemensah.com/blog/recoding) in R. 

Then, we will read in the Code Book Jackie developed

```{r codebook}
#filepath & here function takes everything in green & helps R locate the correct file path
filepath <- here("../")
#"../" means one file outside of this file
print(filepath) #double check the filepath is correct
#filename function tells R where the exact file is located

filename <- list.files(path = filepath, pattern = "BQL Master Codebook.xlsx") #which file do we want to read in?

print(filename) #check which file we have selected
#print function means 'show me what is in this file'

#read_excel() reads in Excel files
codebook_demographics <- read_excel(path = here(filepath, filename[1]), sheet = 1) %>% 
  mutate("Source Construct" = "NA")
codebook_anxiety <- read_excel(path = here(filepath, filename[1]), sheet = 2) 
codebook_ryff <- read_excel(path = here(filepath, filename[1]), sheet = 3)
codebook_ryff <- codebook_ryff[,1:5]
codebook_black <- read_excel(path = here(filepath, filename[1]), sheet = 4) %>% 
  mutate("Source Construct" = "NA")
codebook_lgbt <- read_excel(path = here(filepath, filename[1]), sheet = 5) %>% 
  mutate("Source Construct" = "NA")
codebook_action <- read_excel(path = here(filepath, filename[1]), sheet = 6) %>% 
  mutate("Source Construct" = "NA")
codebook_consciousness <- read_excel(path = here(filepath, filename[1]), sheet = 7) %>% 
  mutate("Source Construct" = "NA")
codebook_community <- read_excel(path = here(filepath, filename[1]), sheet = 8) %>% 
  mutate("Source Construct" = "NA")
codebook_hope <- read_excel(path = here(filepath, filename[1]), sheet = 9) %>% 
  mutate("Source Construct" = "NA")
codebook_empowerment <- read_excel(path = here(filepath, filename[1]), sheet = 10) %>% 
  mutate("Source Construct" = "NA")

codebook <- rbind(
  codebook_demographics,
  codebook_anxiety,
  codebook_ryff,
  codebook_black,
  codebook_lgbt,
  codebook_action,
  codebook_consciousness,
  codebook_community,
  codebook_hope,
  codebook_empowerment
)
```


Then we will look at what participants answered when asked about: 
- their Race/Ethnicity (Q36 and Q36_11_TEXT)

```{r race_ethnicity}
race_ethnicity <- pre_survey_clean %>% 
  select(Q1,
         Q36) %>% 
  pivot_longer(
    cols = !Q1, 
    names_to = "Variable Name",
    values_to = "Value"
  ) %>% 
  mutate(Value = strsplit(as.character(Value), ",")) %>% 
    unnest(Value) 

#join the codebook descriptions
race_ethnicity_description <- left_join(x = race_ethnicity, y = codebook) %>% 
  select(-"Source Construct") %>% 
  mutate("Question Text" = "Race") 

race_ethnicity_description$Label[!is.na(race_ethnicity_description$Value) & is.na(race_ethnicity_description$Label)] <- race_ethnicity_description$Value

race_ethnicity_summary <- race_ethnicity_description %>% 
  group_by(Label) %>% 
  summarise(
    Label = Label, 
    n = n(),
  ) %>% 
  ungroup() %>% 
  unique() %>% 
  drop_na() %>% 
  adorn_totals(where = "row", na.rm = TRUE, name = "Total")

race_ethnicity_summary$n[race_ethnicity_summary$Label == "Total"] <- length(unique(race_ethnicity$Q1))

print(race_ethnicity_summary)
```

- Gender (Q34 and Q34_7_TEXT)

```{r gender}
gender <- pre_survey_clean %>% 
  select(Q1,
         Q34,
         Q34_7_TEXT) %>% 
  pivot_longer(
    cols = !Q1, 
    names_to = "Variable Name",
    values_to = "Value"
  ) %>% 
  mutate(Value = strsplit(as.character(Value), ",")) %>% 
    unnest(Value) %>% 
  drop_na(Value)

#join the codebook descriptions
gender_description <- left_join(x = gender, y = codebook) %>% 
  select(-"Source Construct") %>% 
  mutate("Question Text" = "Gender") 

gender_summary <- gender_description %>% 
  group_by(Label) %>% 
  summarise(
    Label = Label, 
    n = n()
  ) %>% 
  ungroup() %>% 
  unique() %>% 
  drop_na() %>% 
  adorn_totals(where = "row", na.rm = TRUE, name = "Total")

gender_summary$n[gender_summary$Label == "Total"] <- length(unique(gender$Q1))

print(gender_summary)
```

- Sexual Orientation (Q35 and Q35_10_TEXT)

```{r sexual_orientation}
sexual_orientation <- pre_survey_clean %>% 
  select(Q1,
         Q35,
         Q35_10_TEXT)  %>% 
  pivot_longer(
    cols = !Q1, 
    names_to = "Variable Name",
    values_to = "Value"
  ) %>% 
  mutate(Value = strsplit(as.character(Value), ",")) %>% 
    unnest(Value) %>% 
  drop_na(Value)

#join the codebook descriptions
sexual_orientation_description <- left_join(x = sexual_orientation, y = codebook) %>% 
  select(-"Source Construct") %>% 
  mutate("Question Text" = "Sexual Orientation") 

sexual_orientation_summary <- sexual_orientation_description %>% 
  group_by(Label) %>% 
  summarise(
    Label = Label, 
    n = n()
  ) %>% 
  ungroup() %>% 
  unique() %>% 
  drop_na() %>% 
  adorn_totals(where = "row", na.rm = TRUE, name = "Total")

sexual_orientation_summary$n[sexual_orientation_summary$Label == "Total"] <- length(unique(sexual_orientation$Q1))

print(sexual_orientation_summary)
```

- Relationship Status (Q5 and Q5_7_TEXT)

```{r relationship_status}
relationship_status <- pre_survey_clean %>% 
  select(Q1,
         Q5,
         Q5_7_TEXT) %>% 
  pivot_longer(
    cols = !Q1, 
    names_to = "Variable Name",
    values_to = "Value"
  ) %>% 
  mutate(Value = strsplit(as.character(Value), ",")) %>% 
    unnest(Value) %>% 
  drop_na(Value)

#join the codebook descriptions
relationship_status_description <- left_join(x = relationship_status, y = codebook) %>% 
  select(-"Source Construct") %>% 
  mutate("Question Text" = "Relationship Status") 

relationship_status_summary <- relationship_status_description %>% 
  group_by(Label) %>% 
  summarise(
    Label = Label, 
    n = n()
  ) %>% 
  ungroup() %>% 
  unique() %>% 
  drop_na() %>% 
  adorn_totals(where = "row", na.rm = TRUE, name = "Total")

relationship_status_summary$n[relationship_status_summary$Label == "Total"] <- length(unique(relationship_status$Q1))

print(relationship_status_summary)
```

- Education (Q4)

```{r education}
education <- pre_survey_clean %>% 
  select(Q1,
         Q4) %>% 
  pivot_longer(
    cols = !Q1, 
    names_to = "Variable Name",
    values_to = "Value"
  ) %>% 
  mutate(Value = strsplit(as.character(Value), ",")) %>% 
    unnest(Value) %>% 
  drop_na(Value)

#join the codebook descriptions
education_description <- left_join(x = education, y = codebook) %>% 
  select(-"Source Construct") %>% 
  mutate("Question Text" = "Education") 

education_summary <- education_description %>% 
  group_by(Label) %>% 
  summarise(
    Label = Label, 
    n = n()
  ) %>% 
  ungroup() %>% 
  unique() %>% 
  drop_na() %>% 
  adorn_totals(where = "row", na.rm = TRUE, name = "Total")

education_summary$n[education_summary$Label == "Total"] <- length(unique(education$Q1))

print(education_summary)
```

- Employment (Q41 and Q41_4_TEXT)

```{r employment}
employment <- pre_survey_clean %>% 
  select(Q1,
         Q41,
         Q41_4_TEXT) %>% 
  pivot_longer(
    cols = !Q1, 
    names_to = "Variable Name",
    values_to = "Value"
  ) %>% 
  mutate(Value = strsplit(as.character(Value), ",")) %>% 
    unnest(Value) %>% 
  drop_na(Value)

#join the codebook descriptions
employment_description <- left_join(x = employment, y = codebook) %>% 
  select(-"Source Construct") %>% 
  mutate("Question Text" = "Employment") 

employment_summary <- employment_description %>% 
  group_by(Label) %>% 
  summarise(
    Label = Label, 
    n = n()
  ) %>% 
  ungroup() %>% 
  unique() %>% 
  drop_na() %>% 
  adorn_totals(where = "row", na.rm = TRUE, name = "Total")

employment_summary$n[employment_summary$Label == "Total"] <- length(unique(employment$Q1))

print(employment_summary)


```

- Income (Q6)

```{r income}
income <- pre_survey_clean %>% 
  select(Q1,
         Q6) %>% 
  pivot_longer(
    cols = !Q1, 
    names_to = "Variable Name",
    values_to = "Value"
  ) %>% 
  mutate(Value = strsplit(as.character(Value), ",")) %>% 
    unnest(Value) %>% 
  drop_na(Value)

#join the codebook descriptions
income_description <- left_join(x = income, y = codebook) %>% 
  select(-"Source Construct") %>% 
  mutate("Question Text" = "Income") 

income_summary <- income_description %>% 
  group_by(Label) %>% 
  summarise(
    Label = Label, 
    n = n()
  ) %>% 
  ungroup() %>% 
  unique() %>% 
  drop_na() %>% 
  adorn_totals(where = "row", na.rm = TRUE, name = "Total")

income_summary$n[income_summary$Label == "Total"] <- length(unique(income$Q1))

print(income_summary)
```

- Critical Action

Q17_1 through Q17_5

```{r critical_action1}
political_action <- pre_survey_clean %>% 
  select(Q1,
         Q17_1
         
         ) %>% 
  pivot_longer(
    cols = !Q1, 
    names_to = "Variable Name",
    values_to = "Value"
  ) %>% 
  mutate(Value = strsplit(as.character(Value), ",")) %>% 
    unnest(Value) %>% 
  drop_na(Value)

#join the codebook descriptions
political_action_description <- left_join(x = political_action, y = codebook) %>% 
  select(-"Source Construct") %>% 
  mutate("Question Text" = "Critical Action") 

political_action_summary <- political_action_description %>% 
  group_by(Label) %>% 
  summarise(
    Label = Label, 
    n = n()
  ) %>% 
  ungroup() %>% 
  unique() %>% 
  drop_na() %>% 
  adorn_totals(where = "row", na.rm = TRUE, name = "Total")

political_action_summary$n[political_action_summary$Label == "Total"] <- length(unique(political_action$Q1))

print(political_action_summary)
```

```{r critical_action2}
political_action <- pre_survey_clean %>% 
  select(Q1,
         Q17_2
         ) %>% 
  pivot_longer(
    cols = !Q1, 
    names_to = "Variable Name",
    values_to = "Value"
  ) %>% 
  mutate(Value = strsplit(as.character(Value), ",")) %>% 
    unnest(Value) %>% 
  drop_na(Value)

#join the codebook descriptions
political_action_description <- left_join(x = political_action, y = codebook) %>% 
  select(-"Source Construct") %>% 
  mutate("Question Text" = "Critical Action") 

political_action_summary <- political_action_description %>% 
  group_by(Label) %>% 
  summarise(
    Label = Label, 
    n = n()
  ) %>% 
  ungroup() %>% 
  unique() %>% 
  drop_na() %>% 
  adorn_totals(where = "row", na.rm = TRUE, name = "Total")

political_action_summary$n[political_action_summary$Label == "Total"] <- length(unique(political_action$Q1))

print(political_action_summary)
```

```{r critical_action3}
political_action <- pre_survey_clean %>% 
  select(Q1,
         Q17_3
         ) %>% 
  pivot_longer(
    cols = !Q1, 
    names_to = "Variable Name",
    values_to = "Value"
  ) %>% 
  mutate(Value = strsplit(as.character(Value), ",")) %>% 
    unnest(Value) %>% 
  drop_na(Value)

#join the codebook descriptions
political_action_description <- left_join(x = political_action, y = codebook) %>% 
  select(-"Source Construct") %>% 
  mutate("Question Text" = "Critical Action") 

political_action_summary <- political_action_description %>% 
  group_by(Label) %>% 
  summarise(
    Label = Label, 
    n = n()
  ) %>% 
  ungroup() %>% 
  unique() %>% 
  drop_na() %>% 
  adorn_totals(where = "row", na.rm = TRUE, name = "Total")

political_action_summary$n[political_action_summary$Label == "Total"] <- length(unique(political_action$Q1))

print(political_action_summary)
```

```{r critical_action4}
political_action <- pre_survey_clean %>% 
  select(Q1,
         Q17_4
         ) %>% 
  pivot_longer(
    cols = !Q1, 
    names_to = "Variable Name",
    values_to = "Value"
  ) %>% 
  mutate(Value = strsplit(as.character(Value), ",")) %>% 
    unnest(Value) %>% 
  drop_na(Value)

#join the codebook descriptions
political_action_description <- left_join(x = political_action, y = codebook) %>% 
  select(-"Source Construct") %>% 
  mutate("Question Text" = "Critical Action") 

political_action_summary <- political_action_description %>% 
  group_by(Label) %>% 
  summarise(
    Label = Label, 
    n = n()
  ) %>% 
  ungroup() %>% 
  unique() %>% 
  drop_na() %>% 
  adorn_totals(where = "row", na.rm = TRUE, name = "Total")

political_action_summary$n[political_action_summary$Label == "Total"] <- length(unique(political_action$Q1))

print(political_action_summary)
```

```{r critical_action5}
political_action <- pre_survey_clean %>% 
  select(Q1,
         Q17_5
         ) %>% 
  pivot_longer(
    cols = !Q1, 
    names_to = "Variable Name",
    values_to = "Value"
  ) %>% 
  mutate(Value = strsplit(as.character(Value), ",")) %>% 
    unnest(Value) %>% 
  drop_na(Value)

#join the codebook descriptions
political_action_description <- left_join(x = political_action, y = codebook) %>% 
  select(-"Source Construct") %>% 
  mutate("Question Text" = "Critical Action") 

political_action_summary <- political_action_description %>% 
  group_by(Label) %>% 
  summarise(
    Label = Label, 
    n = n()
  ) %>% 
  ungroup() %>% 
  unique() %>% 
  drop_na() %>% 
  adorn_totals(where = "row", na.rm = TRUE, name = "Total")

political_action_summary$n[political_action_summary$Label == "Total"] <- length(unique(political_action$Q1))

print(political_action_summary)
```

# Scales

TASK FOR JACKIE: Double-check that descriptions are correct for analysis

Scale
Measure
Which Weeks to Pull
How Many People per timepoint
Helpful to know their codes (e.g. Las, Bell, Tor)

## PHQ-4 Anxiety & Depression

PHQ-4 Anxiety & Depression (ALL ITEMS in Q8.Q8_1, Q8_2, Q8_3, and Q8_4)
- Averaging the total of this measure's items for 3 people
- Reporting the mean average scores in Pre-Survey > Week 2 > Week 4 > Week 6 > Post-Test > Follow-Up 
- Group by person & average the scores

MANUSCRIPT TEXT:
- H1a: Participants were hypothesized to report lower scores on the PHQ-4 Anxiety & Depression scale at post-survey compared to pre-survey. Descriptive analysis showed that at pre-test, the
mean average score was ## (n=3), at week 2, the average score was ##(n=3), at week 4, the mean average score was ## (n=2), at Week 6 the average was ## (n=1), at post-test, the average was ## (n=1), and at follow-up the mean average score was ## (n=1)

```{r pre_anxiety}
pre_anxiety <- pre_survey_clean %>% 
  select(
    Q1, 
    Q8_1,
    Q8_2,
    Q8_3,
    Q8_4
  ) %>% 
  mutate(
    Q8_1 = as.numeric(Q8_1),
    Q8_2 = as.numeric(Q8_2),
    Q8_3 = as.numeric(Q8_3),
    Q8_4 = as.numeric(Q8_4),
  )

n <- (ncol(pre_anxiety) - 1)

pre_anxiety$average <- (pre_anxiety$Q8_1 + pre_anxiety$Q8_2 + pre_anxiety$Q8_3 + pre_anxiety$Q8_4) / n

print(pre_anxiety)
```


```{r}
pre_anxiety_mean_avg <- round(mean(pre_anxiety$average), digits = 2)
print(pre_anxiety_mean_avg)
```

```{r week2_anxiety}
week2_anxiety <- week2_clean %>% 
  select(
    Q1, 
    Q8_1,
    Q8_2,
    Q8_3,
    Q8_4
  ) %>% 
  
  #keep only the first digit in each column 
  mutate(Q8_1 = gsub("(^\\d{1}).*", "\\1", Q8_1),
         Q8_2 = gsub("(^\\d{1}).*", "\\1", Q8_2),
         Q8_3 = gsub("(^\\d{1}).*", "\\1", Q8_3),
         Q8_4 = gsub("(^\\d{1}).*", "\\1", Q8_4)) %>% 
  mutate(
    Q8_1 = as.numeric(Q8_1),
    Q8_2 = as.numeric(Q8_2),
    Q8_3 = as.numeric(Q8_3),
    Q8_4 = as.numeric(Q8_4),
  )

n <- (ncol(week2_anxiety) - 1)

week2_anxiety$average <- (week2_anxiety$Q8_1 + week2_anxiety$Q8_2 + week2_anxiety$Q8_3 + week2_anxiety$Q8_4) / n

print(week2_anxiety)
```


```{r}
week2_anxiety_mean_avg <- round(mean(week2_anxiety$average), digits = 2)
print(week2_anxiety_mean_avg)
```

```{r week4_anxiety}
week4_anxiety <- week4_clean %>% 
  select(
    Q1, 
    Q8_1,
    Q8_2,
    Q8_3,
    Q8_4
  ) %>% 
  
  #keep only the first digit in each column 
  mutate(Q8_1 = gsub("(^\\d{1}).*", "\\1", Q8_1),
         Q8_2 = gsub("(^\\d{1}).*", "\\1", Q8_2),
         Q8_3 = gsub("(^\\d{1}).*", "\\1", Q8_3),
         Q8_4 = gsub("(^\\d{1}).*", "\\1", Q8_4)) %>% 
  mutate(
    Q8_1 = as.numeric(Q8_1),
    Q8_2 = as.numeric(Q8_2),
    Q8_3 = as.numeric(Q8_3),
    Q8_4 = as.numeric(Q8_4),
  )

n <- (ncol(week4_anxiety) - 1)

week4_anxiety$average <- (week4_anxiety$Q8_1 + week4_anxiety$Q8_2 + week4_anxiety$Q8_3 + week4_anxiety$Q8_4) / n

print(week4_anxiety)
```


```{r}
week4_anxiety_mean_avg <- round(mean(week4_anxiety$average), digits = 2)
print(week4_anxiety_mean_avg)
```

```{r week6_anxiety}
week6_anxiety <- week6_clean %>% 
  clean_names() %>% 
  select(
    q1, 
    phq_4_1,
    phq_4_2,
    phq_4_3,
    phq_4_4
  ) %>% 
  
  #keep only the first digit in each column 
  mutate(phq_4_1 = gsub("(^\\d{1}).*", "\\1", phq_4_1),
         phq_4_2 = gsub("(^\\d{1}).*", "\\1", phq_4_2),
         phq_4_3 = gsub("(^\\d{1}).*", "\\1", phq_4_3),
         phq_4_4 = gsub("(^\\d{1}).*", "\\1", phq_4_4)) %>% 
  mutate(
    phq_4_1 = as.numeric(phq_4_1),
    phq_4_2 = as.numeric(phq_4_2),
    phq_4_3 = as.numeric(phq_4_3),
    phq_4_4 = as.numeric(phq_4_4),
  )

n <- (ncol(week6_anxiety) - 1)

week6_anxiety$average <- (week6_anxiety$phq_4_1 + week6_anxiety$phq_4_2 + week6_anxiety$phq_4_3 + week6_anxiety$phq_4_4) / n

print(week6_anxiety)
```

```{r follow_up_anxiety}
follow_up_anxiety <- follow_up_clean %>% 
  select(
    Q1, 
    Q8_1,
    Q8_2,
    Q8_3,
    Q8_4
  ) %>% 
  
  #keep only the first digit in each column 
  mutate(Q8_1 = gsub("(^\\d{1}).*", "\\1", Q8_1),
         Q8_2 = gsub("(^\\d{1}).*", "\\1", Q8_2),
         Q8_3 = gsub("(^\\d{1}).*", "\\1", Q8_3),
         Q8_4 = gsub("(^\\d{1}).*", "\\1", Q8_4)) %>% 
  mutate(
    Q8_1 = as.numeric(Q8_1),
    Q8_2 = as.numeric(Q8_2),
    Q8_3 = as.numeric(Q8_3),
    Q8_4 = as.numeric(Q8_4),
  )

n <- (ncol(follow_up_anxiety) - 1)

follow_up_anxiety$average <- (follow_up_anxiety$Q8_1 + follow_up_anxiety$Q8_2 + follow_up_anxiety$Q8_3 + follow_up_anxiety$Q8_4) / n

print(follow_up_anxiety)
```

```{r mean_average_summary}
# R program to illustrate 
# data frame from vector 

#how many surveys to summarize
Survey <- c("Pre-Survey", 
            "Week 2", 
            "Week 4", 
            "Week 6", 
            "Follow-Up") 

#how many participants per survey ?
Participants <- c(nrow(pre_anxiety), 
            nrow(week2_anxiety),
            nrow(week4_anxiety),
            nrow(week6_anxiety),
            nrow(follow_up_anxiety)) 

#mean average score per week
MeanAverage <- c(pre_anxiety_mean_avg, 
                  week2_anxiety_mean_avg, 
                  week4_anxiety_mean_avg, 
                  NA,
                  NA)

#create the data frame 
class.df <- data.frame(Survey,
                      Participants,
                      MeanAverage) 
print(class.df)
```


## Ryff Psychological Wellbeing Scale

All Q9 questions

H1b: Participants were hypothesized to report higher scores on the Ryff Psychological Wellbeing Scale at post-test and follow-up than pre-test. Descriptive analysis showed that at pre-test, the mean average score was ##, at post-test the mean average was ##, and at follow-up, the mean average score was ## suggesting…. 

```{r pre_rhyff}
pre_anxiety <- pre_survey_clean %>% 
  select(
    Q1, 
    Q8_1,
    Q8_2,
    Q8_3,
    Q8_4
  ) %>% 
  mutate(
    Q8_1 = as.numeric(Q8_1),
    Q8_2 = as.numeric(Q8_2),
    Q8_3 = as.numeric(Q8_3),
    Q8_4 = as.numeric(Q8_4),
  )

n <- (ncol(pre_anxiety) - 1)

pre_anxiety$average <- (pre_anxiety$Q8_1 + pre_anxiety$Q8_2 + pre_anxiety$Q8_3 + pre_anxiety$Q8_4) / n

print(pre_anxiety)
```


H1c: Participants were hypothesized to report higher scores on the Black Identity Development Scale at post-test and follow-up than at pre-test. Descriptive analysis showed that at pre-test, the mean average score was ##, at post-test the mean average was ##, and at follow-up, the mean average score was ##, suggesting... 

H1d: Participants were hypothesized to report higher scores on the LGBT Positive Identity Measure at post-test and follow-up than at pre-test. Descriptive analysis showed that at pre-test, the mean average score was ##, at post-test the mean average was ##, and at follow-up, the mean average score was ##, suggesting… 

H1e: Participants were hypothesized to report greater self-compassion at post-test and follow-up compared to pre-test, as measured by the Self-Compassion Scale. Descriptive analysis showed that at pre-test, the mean average score was ##, at post-test the mean average was ##, and at follow-up, the mean average score was ##, suggesting... 

H1f: Participants were hypothesized to report increased scores on the Short Critical Consciousness Scale and the Contemporary Critical Consciousness Measures I and II at post-test and follow-up compared to pre-test. Descriptive analysis showed that pre-test mean scores for each scale were ##, ##, and ## respectively, post-test scores were ##, ##, and ##, and follow-up scores were ##, ##, and ##, suggesting... 

H1g: Participants were hypothesized to report higher scores on the Collective Self-Esteem Scale at post-test and follow-up than at pre-test. Descriptive analysis showed that at pre-test, the mean average score was ##, at post-test the mean average was ##, and at follow-up, the mean average score was ##, suggesting... 

H1h: Participants were hypothesized to report increased Radical Hope from pre- to post-test and follow-up. Descriptive analysis showed that at pre-test, the mean average score was ##, at post-test the mean average was ##, and at follow-up, the mean average score was ##, suggesting... 

H1i: Participants were hypothesized to report higher scores on the Individual-Community Related Empowerment Measure at post-test and follow-up than at pre-test. Descriptive analysis showed that at pre-test, the mean average score was ##, at post-test the mean average was ##, and at follow-up, the mean average score was ##, suggesting... 