---
title: "Manipulation Checks and Acceptability & Feasibility "
author: "Jackie & Mia"
date: "2025-05-14"
output: html_document
---

# Workflow

Run this file after `rq1.Rmd` and `rq2.Rmd` because those files contain essential context for this project. 

# Objective

To complete the Manipulation Checks as well as the Acceptability & Feasibility, we must average the scores of specific questions from each weekly survey. For the Manipulation Checks, each week has 3-4 items to average the scores from Week 1 - Week 6. For the Acceptability & Feasibility, there are 12 items to average from the Week 6 data only. No reverse coding needed. 

This is the last step of the dissertation project data analysis phase. 

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = FALSE,
	message = FALSE,
	warning = FALSE
)
options(knitr.duplicate.label = "allow",
        scipen = 999)

#install packages if necessary, then load libraries
if (!require(librarian)){
  install.packages("librarian")
  library(librarian)
}
librarian::shelf(
  #expss, #to make tables
  here, #to build file paths
  janitor, #for column name cleaning
  lubridate, #for working with dates 
  readxl, #read in Excel files
  stringr, #to clean data 
  tidyr, #data cleaning
  tidyverse, #general data cleaning functions and collection of common packages
  dplyr, #case_match
  writexl #save Excel files
  )
```

# Read in Survey Data
- The raw Excel data was exported from Qualtrics 
- This is the same survey data used in `rq1.Rmd` and `rq2.Rmd`

```{r read_in_data}
filepath <- here("../")
print(filepath) #double check the filepath is correct

filename <- list.files(path = filepath, pattern = "BQL Survey Data - CLEAN - FINAL.xlsx") 
print(filename) #check which file we have selected

#read in Excel files
pre_survey <- read_excel(path = here(filepath, filename[1]), sheet = "Pre-Survey") 
week1 <- read_excel(path = here(filepath, filename[1]), sheet = "Week 1") 
week2 <- read_excel(path = here(filepath, filename[1]), sheet = "Week 2")
week3 <- read_excel(path = here(filepath, filename[1]), sheet = "Week 3")
week4 <- read_excel(path = here(filepath, filename[1]), sheet = "Week 4")
week5 <- read_excel(path = here(filepath, filename[1]), sheet = "Week 5")
week6 <- read_excel(path = here(filepath, filename[1]), sheet = "Week 6")
post_survey <- read_excel(path = here(filepath, filename[1]), sheet = "Post-Survey")
follow_up <- read_excel(path = here(filepath, filename[1]), sheet = "FollowUp")
```

# Clean the data 
Week 1 had no real data

Note that this cleaning process is identical to that used in `rq1.Rmd` and `rq2.Rmd`

```{r}
pre_survey_clean <- pre_survey %>% 
  filter(
    Q1 == "BELL" | Q1 == "BER" | Q1 == "LAS"
  ) %>% 
  drop_na(Q4)

week2_clean <- week2 %>% 
  mutate(
    Q1 = toupper(Q1)
  ) %>% 
  filter(
    Q1 == "BELL" | Q1 == "LAS" | Q1 == "TOR"
  )

week3_clean <- week3 %>% 
  mutate(
    Q1 = toupper(Q1)
  ) %>% 
  filter(
    Q1 == "BAL" | Q1 == "LAS" | Q1 == "TOR"
  )

week4_clean <- week4 %>% 
  mutate(
    Q1 = toupper(Q1)
  ) %>% 
  filter(
    Q1 == "LAS" | Q1 == "TOR"
  )

week5_clean <- week5 %>% 
  mutate(
    Q1 = toupper(Q1)
  ) %>% 
  filter(
    Q1 == "LAS" | Q1 == "TOR"
  )

week6_clean <- week6 %>% 
  mutate(
    Q1 = toupper(Q1)
  ) %>% 
  filter(
    Q1 == "LAS"
  )

post_survey_clean <- post_survey %>% 
  mutate(
    Q1 = toupper(Q1)
  ) %>% 
  filter(
    Q1 == "LAS"
  )

follow_up_clean <- follow_up %>% 
  mutate(
    Q1 = toupper(Q1)
  ) %>% 
  filter(
    Q1 == "TOR"
  )
```

#Manipulation Checks

##Week 1

Missing all Week 1 data

##Week 2 (n=3)

Item 1-3

```{r}
item <- week2_clean %>% 
  select(
    Q1, 
    starts_with("Q48_")
  ) %>% 
  #keep only numeric digits
  mutate(across(starts_with(c("Q48")), ~ gsub("[^0-9.-]+", "", .))) %>% 
  #change class to numeric for all columns that start with Q48
  mutate_at(vars(starts_with("Q48_")), funs(as.numeric(as.character(.)))) 

#calculate each question's mean
item_means <- item %>% 
  summarise_each(funs(mean( .,na.rm = TRUE)))

#rename average row
item_means$Q1[is.na(item_means$Q1)] <- "Average"

#append means to original scores
item_with_means <- rbind(item, item_means)

#examine the output
print(item_with_means)
```

##Week 3 (n=3)

Item 1-3

```{r}
item <- week3_clean %>% 
  select(
    Q1, 
    starts_with("Q48_")
  ) %>% 
  #keep only numeric digits
  mutate(across(starts_with(c("Q48")), ~ gsub("[^0-9.-]+", "", .))) %>% 
  #change class to numeric for all columns that start with Q48
  mutate_at(vars(starts_with("Q48_")), funs(as.numeric(as.character(.)))) 

#calculate each question's mean
item_means <- item %>% 
  summarise_each(funs(mean( .,na.rm = TRUE)))

#rename average row
item_means$Q1[is.na(item_means$Q1)] <- "Average"

#append means to original scores
item_with_means <- rbind(item, item_means)

#examine the output
print(item_with_means)
```

##Week 4 (n=2)

Item 1-4

```{r}
item <- week4_clean %>% 
  select(
    Q1, 
    starts_with("Q48_")
  ) %>% 
  #keep only numeric digits
  mutate(across(starts_with(c("Q48")), ~ gsub("[^0-9.-]+", "", .))) %>% 
  #change class to numeric for all columns that start with Q48
  mutate_at(vars(starts_with("Q48_")), funs(as.numeric(as.character(.)))) 

#calculate each question's mean
item_means <- item %>% 
  summarise_each(funs(mean( .,na.rm = TRUE)))

#rename average row
item_means$Q1[is.na(item_means$Q1)] <- "Average"

#append means to original scores
item_with_means <- rbind(item, item_means)

#examine the output
print(item_with_means)
```

##Week 5 (n=2)

Item 1-3

```{r}
item <- week5_clean %>% 
  select(
    Q1, 
    starts_with("Q48_")
  ) %>% 
  #keep only numeric digits
  mutate(across(starts_with(c("Q48")), ~ gsub("[^0-9.-]+", "", .))) %>% 
  #change class to numeric for all columns that start with Q48
  mutate_at(vars(starts_with("Q48_")), funs(as.numeric(as.character(.)))) 

#calculate each question's mean
item_means <- item %>% 
  summarise_each(funs(mean( .,na.rm = TRUE)))

#rename average row
item_means$Q1[is.na(item_means$Q1)] <- "Average"

#append means to original scores
item_with_means <- rbind(item, item_means)

#examine the output
print(item_with_means)
```

##Week 6 (n=1)

Item 1-3

```{r}
item <- week6_clean %>% 
  select(
    Q1, 
    starts_with("Q48_")
  ) %>% 
  #keep only numeric digits
  mutate(across(starts_with(c("Q48")), ~ gsub("[^0-9.-]+", "", .))) %>% 
  #change class to numeric for all columns that start with Q48
  mutate_at(vars(starts_with("Q48_")), funs(as.numeric(as.character(.)))) 
```


#Acceptability & Feasibility (n=1)

Use Week 6 survey data only 

Items 1-12

Average the score from each item

```{r}
item <- week6_clean %>% 
  select(
    Q1, 
    starts_with("Q55_")
  ) %>% 
  #keep only numeric digits (not hyphens)
  mutate(across(starts_with(c("Q55")), ~ gsub("[^0-9.]+", "", .))) %>% 
  #change class to numeric for all columns that start with Q48
  mutate_at(vars(starts_with("Q55_")), funs(as.numeric(as.character(.)))) %>% 
  pivot_longer(
    cols = !Q1,
    names_to = "Variable Name",
    values_to = "Value"
  ) %>% 
  unnest()

#calculate each question's mean
item_means <- item %>%
  summarise_each(funs(mean( .,na.rm = TRUE)))

#rename average row
item_means$Q1[is.na(item_means$Q1)] <- "Average"

#append means to original scores
item_with_means <- rbind(item, item_means)

#examine the output
print(item_with_means)
```

Results were transferred into an external Excel sheet for further formatting for the final dissertation defense deliverables. 


