---
title: "power_test"
output: html_document
date: "2024-04-21"
---

# Objective

To run a power analysis for Jacquelyn Chin's 2024 dissertation draft. 

Tutorial can be found here: https://ladal.edu.au/pwr.html#What_determines_if_you_find_an_effect

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = FALSE,
	message = FALSE,
	warning = FALSE
)
options(knitr.duplicate.label = "allow",
        scipen = 999)

# set options
options(stringsAsFactors = F)         # no automatic conversion of factors
options("scipen" = 100, "digits" = 4) # suppress math annotation
options(max.print=1000)               # print max 1000 results

#install packages if necessary, then load libraries
if (!require(librarian)){
  install.packages("librarian")
  library(librarian)
}
librarian::shelf(
  tidyverse,
  pwr,
  lme4,
  sjPlot,
  simr,
  effectsize,
  DT,
  knitr,
  flextable,
  pacman,
  
  remotes
  )

pacman::p_load_gh("trinker/entity")

# install.packages("remotes")
remotes::install_github("rlesur/klippy")

# activate klippy for copy-to-clipboard button
klippy::klippy()
```

# One-way ANOVA

## Known effect size + unknown sample size 

Let check how to calculate the necessary sample size for each group for a one-way ANOVA that compares 5 groups (k) and that has a power of 0.80 (80 percent), when the effect size is moderate (f = 0.25) and the significance level is 0.05 (5 percent)..

```{r}
# load package
library(pwr)

# calculate minimal sample size
pwr.anova.test(k=4,           # 4 groups are compared
               f=.4,          # large effect size
               sig.level=.05,  # alpha/sig. level = .05
               power=.8)       # confint./power = .8
```
## Known sample size + unknown effect size 

Let’s check how we could calculate the power if we had already collected data (with 30 participants in each group) and we want to report the power of our analysis (and let us assume that the effect size was medium).


```{r}
# calculate minimal sample size
pwr.anova.test(k=4,            # 4 groups are compared
               f=.25,          # moderate effect size
               sig.level=.05,  # alpha/sig. level = .05
               n=30) 
```

In this case our analysis would only have a power or 66.8 percent. This means that we would only detect a medium sized effect in 66.7 percent of cases (which is considered insufficient).