---
title: "RQ2"
author: "Jackie & Mia"
date: "2025-05-10"
output: html_document
---

# Objective

To complete Research Question 2, which compares item scores in each week's module. 

For example, Week 1 (Radical Healing) averages each participant's score for each item from Pre-Survey and Week 1. Then, we compare the average score from Pre-Survey to Week 1 to analyze changes over time. 

For Week 2 (Critical Consciousness), we compare the average score from Pre-Survey to Week 2 results. 

For Week 3 (Radical Hope), we compare the average score from Pre-Survey to Week 3, and so on. 

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = FALSE,
	message = FALSE,
	warning = FALSE
)
options(knitr.duplicate.label = "allow",
        scipen = 999)

#install packages if necessary, then load libraries
if (!require(librarian)){
  install.packages("librarian")
  library(librarian)
}
librarian::shelf(
  #expss, #to make tables
  here, #to build file paths
  janitor, #for column name cleaning
  lubridate, #for working with dates 
  readxl, #read in Excel files
  stringr, #to clean data 
  tidyr, #data cleaning
  tidyverse, #general data cleaning functions and collection of common packages
  dplyr, #case_match
  writexl #save Excel files
  )
```

# Read in Survey Data
- The raw Excel data was exported from Qualtrics 
- This is the same survey data used in `rq1.Rmd`

```{r read_in_data}
#filepath & here function takes everything in green & helps R locate the correct file path
filepath <- here("../")
#"../" means one file outside of this file
print(filepath) #double check the filepath is correct
#filename function tells R where the exact file is located

filename <- list.files(path = filepath, pattern = "BQL Survey Data - CLEAN - FINAL.xlsx") #which file do we want to read in?

print(filename) #check which file we have selected
#print function means 'show me what is in this file'

#read_excel() reads in Excel files
pre_survey <- read_excel(path = here(filepath, filename[1]), sheet = 1) 
week1 <- read_excel(path = here(filepath, filename[1]), sheet = 2) 
week2 <- read_excel(path = here(filepath, filename[1]), sheet = 3)
week3 <- read_excel(path = here(filepath, filename[1]), sheet = 4)
week4 <- read_excel(path = here(filepath, filename[1]), sheet = 5)
week5 <- read_excel(path = here(filepath, filename[1]), sheet = 6)
week6 <- read_excel(path = here(filepath, filename[1]), sheet = 7)
post_survey <- read_excel(path = here(filepath, filename[1]), sheet = 8)
follow_up <- read_excel(path = here(filepath, filename[1]), sheet = 9)
```

# Clean the data 
We want to drop the "dummy" participants from pre-survey results 
- AKA we want to remove fake data based on Q1

Week 1 had no real data

Refer to BQL Survey Data - CLEAN - FINAL to see how many real participants completed each week's survey

Note that this cleaning process is identical to that used in `rq1.Rmd`

```{r}
pre_survey_clean <- pre_survey %>% 
  filter(
    Q1 == "BELL" | Q1 == "BER" | Q1 == "LAS"
  ) %>% 
  drop_na(Q4)

week2_clean <- week2 %>% 
  mutate(
    Q1 = toupper(Q1)
  ) %>% 
  filter(
    Q1 == "BELL" | Q1 == "LAS" | Q1 == "TOR"
  )

week3_clean <- week3 %>% 
  mutate(
    Q1 = toupper(Q1)
  ) %>% 
  filter(
    Q1 == "BAL" | Q1 == "LAS" | Q1 == "TOR"
  )

week4_clean <- week4 %>% 
  mutate(
    Q1 = toupper(Q1)
  ) %>% 
  filter(
    Q1 == "LAS" | Q1 == "TOR"
  )

week5_clean <- week5 %>% 
  mutate(
    Q1 = toupper(Q1)
  ) %>% 
  filter(
    Q1 == "LAS" | Q1 == "TOR"
  )

week6_clean <- week6 %>% 
  mutate(
    Q1 = toupper(Q1)
  ) %>% 
  filter(
    Q1 == "LAS"
  )

post_survey_clean <- post_survey %>% 
  mutate(
    Q1 = toupper(Q1)
  ) %>% 
  filter(
    Q1 == "LAS"
  )

follow_up_clean <- follow_up %>% 
  mutate(
    Q1 = toupper(Q1)
  ) %>% 
  filter(
    Q1 == "TOR"
  )
```

#Read in Codebook 

- This is the same codebook used in `rq1.Rmd`

```{r codebook}
#filepath & here function takes everything in green & helps R locate the correct file path
filepath <- here("../")
#"../" means one file outside of this file
print(filepath) #double check the filepath is correct
#filename function tells R where the exact file is located

filename <- list.files(path = filepath, pattern = "BQL Master Codebook.xlsx") #which file do we want to read in?

print(filename) #check which file we have selected
#print function means 'show me what is in this file'

#4 columns
codebook_demographics <- read_excel(path = here(filepath, filename[1]), sheet = "Demographics") %>% 
  mutate("Source Construct" = NA,
         "Reverse" = NA,
         "New Value" = NA)
codebook_black <- read_excel(path = here(filepath, filename[1]), sheet = "Black Identity") %>% 
  mutate("Source Construct" = NA,
         "Reverse" = NA,
         "New Value" = NA)
codebook_lgbt <- read_excel(path = here(filepath, filename[1]), sheet = "LGBTQIA+ Identity Scale") %>% 
  mutate("Source Construct" = NA,
         "Reverse" = NA,
         "New Value" = NA)
codebook_action <- read_excel(path = here(filepath, filename[1]), sheet = "Critical Action") %>% 
  mutate("Source Construct" = NA,
         "Reverse" = NA,
         "New Value" = NA)
codebook_hope <- read_excel(path = here(filepath, filename[1]), sheet = "Radical Hope") %>% 
  mutate("Source Construct" = NA,
         "Reverse" = NA,
         "New Value" = NA)
codebook_empowerment <- read_excel(path = here(filepath, filename[1]), sheet = "Empowerment") %>% 
  mutate("Source Construct" = NA,
         "Reverse" = NA,
         "New Value" = NA)

#source construct = 5 columns
codebook_anxiety <- read_excel(path = here(filepath, filename[1]), sheet = "PHQ-4 Anxiety Depression") %>%
  mutate() %>% 
  mutate("Reverse" = NA,
         "New Value" = NA)
codebook_ryff <- read_excel(path = here(filepath, filename[1]), sheet = "Ryff Wellbeing") %>% 
  mutate("Reverse" = NA,
         "New Value" = NA)

#reverse-coding = 6 columns
codebook_consciousness <- read_excel(path = here(filepath, filename[1]), sheet = "Critical Consciousness") %>% 
  mutate("Source Construct" = NA)
codebook_community <- read_excel(path = here(filepath, filename[1]), sheet = "Collective Self-Esteem") %>% 
  mutate("Source Construct" = NA)

codebook <- rbind(
  codebook_demographics,
  codebook_anxiety,
  codebook_ryff,
  codebook_black,
  codebook_lgbt,
  codebook_action,
  codebook_consciousness,
  codebook_community,
  codebook_hope,
  codebook_empowerment
) %>% 
  rename(NewValue = "New Value") %>% 
  #if_else() must work with characters
  mutate(CombinedValues = if_else(is.na(NewValue), Value, as.character(NewValue)))
```

#Week 1: Radical Healing

Missing all data from Week 1 survey

#Week 2: Critical Consciousness

n = 3

##Reverse code Week 2 data

Refer to the Results Table Excel sheet to better understand which questions correspond with which week

Pre-Survey

```{r pre_week2}
pre_week2 <- pre_survey_clean %>% 
  select(
    Q1, 
    starts_with("Q18_")
  ) %>% 
  #change class to numeric for all columns that start with "Q18_"
  mutate_at(vars(starts_with("Q18_")), funs(as.numeric(as.character(.)))) %>% 
  #format long data to join to codebook
  pivot_longer(cols = !Q1,
               names_to = "Variable Name",
               values_to = "Value")


#pull out the reverse codes
reverse_codes <- codebook %>% 
  filter(str_detect(Reverse, "Y")) %>% 
  select(
    "Variable Name",
    Value,
    NewValue
  ) %>% 
  mutate(
    Value = as.numeric(Value)
  )

#join the survey data to the codebook 
pre_week2_codebook <- left_join(x = pre_week2, y = reverse_codes) %>% 
  #if_else() must work with characters
  mutate(
    NewValue = as.character(NewValue),
    Value = as.character(Value),
    #identify the correct value to use
    CorrectedValue = if_else(is.na(NewValue), Value, as.character(NewValue)))

#reformat to wide for analysis
pre_week2 <- pre_week2_codebook %>% 
  select(
    -NewValue,
    -Value
  ) %>% 
  rename(Value = CorrectedValue) %>% 
  mutate(Value = as.numeric(Value)) %>% 
  pivot_wider(
    names_from = "Variable Name",
    values_from = "Value"
  )

#calculate each question's mean
pre_week2_means <- pre_week2 %>% 
  summarise_each(funs(mean( .,na.rm = TRUE)))

#rename average row
pre_week2_means$Q1[is.na(pre_week2_means$Q1)] <- "Average"

#append means to original scores
pre_week2_with_means <- rbind(pre_week2, pre_week2_means)

#examine the output
print(pre_week2_with_means)
```

Week 2

We will compare this to the pre-survey data

```{r post_week2}
post_week2 <- week2_clean %>% 
  select(
    Q1, 
    starts_with("Q18_")
  ) %>% 
  #keep only the first digit
  mutate(across(starts_with("Q18_"), ~ gsub("(^\\d{1}).*", "\\1", .))) %>%
  #change class to numeric for all columns that start with "Q18_"
  mutate_at(vars(starts_with("Q18_")), funs(as.numeric(as.character(.)))) %>% 
  #format long data to join to codebook
  pivot_longer(cols = !Q1,
               names_to = "Variable Name",
               values_to = "Value")


#pull out the reverse codes
reverse_codes <- codebook %>% 
  filter(str_detect(Reverse, "Y")) %>% 
  select(
    "Variable Name",
    Value,
    NewValue
  ) %>% 
  mutate(
    Value = as.numeric(Value)
  )

#join the survey data to the codebook 
post_week2_codebook <- left_join(x = post_week2, y = reverse_codes) %>% 
  #if_else() must work with characters
  mutate(
    NewValue = as.character(NewValue),
    Value = as.character(Value),
    CorrectedValue = if_else(is.na(NewValue), Value, as.character(NewValue)))

post_week2 <- post_week2_codebook %>% 
  select(
    -NewValue,
    -Value
  ) %>% 
  rename(Value = CorrectedValue) %>% 
  mutate(Value = as.numeric(Value)) %>% 
  pivot_wider(
    names_from = "Variable Name",
    values_from = "Value"
  )

#calculate each question's mean
post_week2_means <- post_week2 %>% 
  summarise_each(funs(mean( .,na.rm = TRUE)))

#rename average row
post_week2_means$Q1[is.na(post_week2_means$Q1)] <- "Average"

#append means to original scores
post_week2_with_means <- rbind(post_week2, post_week2_means)

print(post_week2_with_means)
```
Now that the data has been cleaned and formatted, isolate each item to compare the pre-survey and week 2 data

##Item 1

Q18_1

```{r}
#pre results
pre_item1 <- pre_week2_with_means %>% 
  select(Q1,
         Q18_1) %>% 
  rename(PreSurvey = Q18_1)

print(pre_item1)

#week 2 (AKA post) results
post_item1 <- post_week2_with_means %>% 
  select(Q1,
         Q18_1) %>% 
  rename(Week2 = Q18_1)

print(post_item1)

#combine pre and post results
item <- full_join(x = pre_item1, y = post_item1) %>% 
  rename(Participant = Q1)
print(item)
```


##Item 10

Note that some items have different question variable names in the pre-survey versus the Week 2 survey 

Pre: Q18_10
Week 2: Q18_2

```{r}
#pre results
pre_item10 <- pre_week2_with_means %>% 
  select(Q1,
         Q18_10) %>% 
  rename(PreSurvey = Q18_10)

print(pre_item10)

#week 2 (AKA post) results
post_item10 <- post_week2_with_means %>% 
  select(Q1,
         Q18_2) %>% 
  rename(Week2 = Q18_2)

print(post_item10)

#combine pre and post results
item <- full_join(x = pre_item10, y = post_item10) %>% 
  rename(Participant = Q1)
print(item)
```

##Item 11

Pre: Q18_11
Week 2: Q18_3

```{r}
#pre results
pre_item11 <- pre_week2_with_means %>% 
  select(Q1,
         Q18_11) %>% 
  rename(PreSurvey = Q18_11)

print(pre_item11)

#week 2 (AKA post) results
post_item11 <- post_week2_with_means %>% 
  select(Q1,
         Q18_3) %>% 
  rename(Week2 = Q18_3)

print(post_item11)

#combine pre and post results
item <- full_join(x = pre_item11, y = post_item11) %>% 
  rename(Participant = Q1)
print(item)
```

##Item 13

Pre: Q18_13
Week 2: Q18_4

```{r}
#pre results
pre_item13 <- pre_week2_with_means %>% 
  select(Q1,
         Q18_13) %>% 
  rename(PreSurvey = Q18_13)

print(pre_item13)

#week 2 (AKA post) results
post_item13 <- post_week2_with_means %>% 
  select(Q1,
         Q18_4) %>% 
  rename(Week2 = Q18_4)

print(post_item13)

#combine pre and post results
item <- full_join(x = pre_item13, y = post_item13) %>% 
  rename(Participant = Q1)
print(item)
```

##Item 15

Pre: Q18_15
Week 2: Q18_5

```{r}
#pre results
pre_item <- pre_week2_with_means %>% 
  select(Q1,
         Q18_15) %>% 
  rename(PreSurvey = Q18_15)

print(pre_item)

#week 2 (AKA post) results
post_item <- post_week2_with_means %>% 
  select(Q1,
         Q18_5) %>% 
  rename(Week2 = Q18_5)

print(post_item)

#combine pre and post results
item <- full_join(x = pre_item, y = post_item) %>% 
  rename(Participant = Q1)
print(item)
```

##Item 16

Pre: Q18_16
Week 2: Q18_6

```{r}
#pre results
pre_item <- pre_week2_with_means %>% 
  select(Q1,
         Q18_16) %>% 
  rename(PreSurvey = Q18_16)

print(pre_item)

#week 2 (AKA post) results
post_item <- post_week2_with_means %>% 
  select(Q1,
         Q18_6) %>% 
  rename(Week2 = Q18_6)

print(post_item)

#combine pre and post results
item <- full_join(x = pre_item, y = post_item) %>% 
  rename(Participant = Q1)
print(item)
```

##Item 17

Pre: Q18_17
Week 2: Q18_7

```{r}
#pre results
pre_item <- pre_week2_with_means %>% 
  select(Q1,
         Q18_17) %>% 
  rename(PreSurvey = Q18_17)

print(pre_item)

#week 2 (AKA post) results
post_item <- post_week2_with_means %>% 
  select(Q1,
         Q18_7) %>% 
  rename(Week2 = Q18_7)

print(post_item)

#combine pre and post results
item <- full_join(x = pre_item, y = post_item) %>% 
  rename(Participant = Q1)
print(item)
```

##Item 18

Pre: Q18_18
Week 2: Q18_8

```{r}
#pre results
pre_item <- pre_week2_with_means %>% 
  select(Q1,
         Q18_18) %>% 
  rename(PreSurvey = Q18_18)

print(pre_item)

#week 2 (AKA post) results
post_item <- post_week2_with_means %>% 
  select(Q1,
         Q18_8) %>% 
  rename(Week2 = Q18_8)

print(post_item)

#combine pre and post results
item <- full_join(x = pre_item, y = post_item) %>% 
  rename(Participant = Q1)
print(item)
```

##Item 20

Pre: Q18_20
Week 2: Q18_9

```{r}
#pre results
pre_item <- pre_week2_with_means %>% 
  select(Q1,
         Q18_20) %>% 
  rename(PreSurvey = Q18_20)

print(pre_item)

#week 2 (AKA post) results
post_item <- post_week2_with_means %>% 
  select(Q1,
         Q18_9) %>% 
  rename(Week2 = Q18_9)

print(post_item)

#combine pre and post results
item <- full_join(x = pre_item, y = post_item) %>% 
  rename(Participant = Q1)
print(item)
```

#Week 3: Radical Hope

n = 3

Not all data needs to be reverse coded

Pre-Survey

```{r pre_week3}
pre_week3 <- pre_survey_clean %>% 
  select(
    Q1, 
    starts_with("Q21_")
  ) %>% 
  #change class to numeric for all columns that start with "Q9_"
  mutate_at(vars(starts_with("Q21_")), funs(as.numeric(as.character(.))))

#calculate each question's mean
pre_week3_means <- pre_week3 %>% 
  summarise_each(funs(mean( .,na.rm = TRUE)))

#rename average row
pre_week3_means$Q1[is.na(pre_week3_means$Q1)] <- "Average"

#append means to original scores
pre_week3_with_means <- rbind(pre_week3, pre_week3_means)

print(pre_week3_with_means)
```

Week 3

```{r post_week3}
post_week3 <- week3_clean %>% 
  select(
    Q1, 
    starts_with("Q21_")
  ) %>% 
  #change class to numeric for all columns that start with "Q9_"
  mutate_at(vars(starts_with("Q21_")), funs(as.numeric(as.character(.))))

#calculate each question's mean
post_week3_means <- post_week3 %>% 
  summarise_each(funs(mean( .,na.rm = TRUE)))

#rename average row
post_week3_means$Q1[is.na(post_week3_means$Q1)] <- "Average"

#append means to original scores
post_week3_with_means <- rbind(post_week3, post_week3_means)

print(post_week3_with_means)
```

##Item 1

Pre: Q21_1
Week 3: Q21_1

```{r}
#pre results
pre_item <- pre_week3_with_means %>% 
  select(Q1,
         Q21_1) %>% 
  rename(PreSurvey = Q21_1)

print(pre_item)

#week 2 (AKA post) results
post_item <- post_week3_with_means %>% 
  select(Q1,
         Q21_1) %>% 
  rename(Week3 = Q21_1)

print(post_item)

#combine pre and post results
item <- full_join(x = pre_item, y = post_item) %>% 
  rename(Participant = Q1)
print(item)
```

##Item 2

Pre: Q21_2
Week 3: Q21_2

```{r}
#pre results
pre_item <- pre_week3_with_means %>% 
  select(Q1,
         Q21_2) %>% 
  rename(PreSurvey = Q21_2)

print(pre_item)

#week 2 (AKA post) results
post_item <- post_week3_with_means %>% 
  select(Q1,
         Q21_2) %>% 
  rename(Week3 = Q21_2)

print(post_item)

#combine pre and post results
item <- full_join(x = pre_item, y = post_item) %>% 
  rename(Participant = Q1)
print(item)
```

##Item 3

Pre: Q21_3
Week 3: Q21_3

```{r}
#pre results
pre_item <- pre_week3_with_means %>% 
  select(Q1,
         Q21_3) %>% 
  rename(PreSurvey = Q21_3)

print(pre_item)

#week 2 (AKA post) results
post_item <- post_week3_with_means %>% 
  select(Q1,
         Q21_3) %>% 
  rename(Week3 = Q21_3)

print(post_item)

#combine pre and post results
item <- full_join(x = pre_item, y = post_item) %>% 
  rename(Participant = Q1)
print(item)
```

##Item 4

Pre: Q21_4
Week 3: Q21_4

```{r}
#pre results
pre_item <- pre_week3_with_means %>% 
  select(Q1,
         Q21_4) %>% 
  rename(PreSurvey = Q21_4)

print(pre_item)

#week 2 (AKA post) results
post_item <- post_week3_with_means %>% 
  select(Q1,
         Q21_4) %>% 
  rename(Week3 = Q21_4)

print(post_item)

#combine pre and post results
item <- full_join(x = pre_item, y = post_item) %>% 
  rename(Participant = Q1)
print(item)
```

##Item 5

Pre: Q21_5
Week 3: Q21_5

```{r}
#pre results
pre_item <- pre_week3_with_means %>% 
  select(Q1,
         Q21_5) %>% 
  rename(PreSurvey = Q21_5)

print(pre_item)

#week 2 (AKA post) results
post_item <- post_week3_with_means %>% 
  select(Q1,
         Q21_5) %>% 
  rename(Week3 = Q21_5)

print(post_item)

#combine pre and post results
item <- full_join(x = pre_item, y = post_item) %>% 
  rename(Participant = Q1)
print(item)
```

##Item 6

Pre: Q21_6
Week 3: Q21_6

```{r}
#pre results
pre_item <- pre_week3_with_means %>% 
  select(Q1,
         Q21_6) %>% 
  rename(PreSurvey = Q21_6)

print(pre_item)

#week 2 (AKA post) results
post_item <- post_week3_with_means %>% 
  select(Q1,
         Q21_6) %>% 
  rename(Week3 = Q21_6)

print(post_item)

#combine pre and post results
item <- full_join(x = pre_item, y = post_item) %>% 
  rename(Participant = Q1)
print(item)
```

#Week 4: Emotional & Social Support

Pre-Survey

```{r pre_week4}
pre_week4 <- pre_survey_clean %>% 
  select(
    Q1, 
    Q9_12,
    Q23_3
  ) %>% 
  #change class to numeric
  mutate(
    Q9_12 = as.numeric(Q9_12),
    Q23_3 = as.numeric(Q23_3)
  )
 

#calculate each question's mean
pre_week4_means <- pre_week4 %>% 
  summarise_each(funs(mean( .,na.rm = TRUE)))

#rename average row
pre_week4_means$Q1[is.na(pre_week4_means$Q1)] <- "Average"

#append means to original scores
pre_week4_with_means <- rbind(pre_week4, pre_week4_means)

print(pre_week4_with_means)
```

Week 4

```{r post_week4}
post_week4 <- week4_clean %>% 
  select(
    Q1, 
    Q9_12,
    Q23_3
  ) %>% 
  #keep only numeric values
  mutate(across(starts_with(c("Q9_", "Q23_")), ~ gsub("[^0-9.-]+", "", .))) %>%  
  #change class to numeric
  mutate(
    Q9_12 = as.numeric(Q9_12),
    Q23_3 = as.numeric(Q23_3)
  )
 
#calculate each question's mean
post_week4_means <- post_week4 %>% 
  summarise_each(funs(mean( .,na.rm = TRUE)))

#rename average row
post_week4_means$Q1[is.na(post_week4_means$Q1)] <- "Average"

#append means to original scores
post_week4_with_means <- rbind(post_week4, post_week4_means)

print(post_week4_with_means)
```

##Item 12

Pre: Q9_12
Week 4: Q9_12

```{r}
#pre results
pre_item <- pre_week4_with_means %>% 
  select(Q1,
         Q9_12) %>% 
  rename(PreSurvey = Q9_12)

print(pre_item)

#week 2 (AKA post) results
post_item <- post_week4_with_means %>% 
  select(Q1,
         Q9_12) %>% 
  rename(Week4 = Q9_12)

print(post_item)

#combine pre and post results
item <- full_join(x = pre_item, y = post_item) %>% 
  rename(Participant = Q1)
print(item)
```

##Item 3

Pre: Q23_3
Week 4: Q23_3

```{r}
#pre results
pre_item <- pre_week4_with_means %>% 
  select(Q1,
         Q23_3) %>% 
  rename(PreSurvey = Q23_3)

print(pre_item)

#week 2 (AKA post) results
post_item <- post_week4_with_means %>% 
  select(Q1,
         Q23_3) %>% 
  rename(Week4 = Q23_3)

print(post_item)

#combine pre and post results
item <- full_join(x = pre_item, y = post_item) %>% 
  rename(Participant = Q1)
print(item)
```

#Week 5: Strength & Resistance 

Pre-Survey missing data

Week 5

Q54_X

```{r post_week5}
post_week5 <- week5_clean %>% 
  select(
    Q1, 
    starts_with("Q54_")
  ) %>% 
  #keep only numeric values
  mutate(across(starts_with(c("Q54_")), ~ gsub("[^0-9.-]+", "", .))) %>%
  #change class to numeric for all columns that start with "Q9_"
  mutate_at(vars(starts_with("Q54_")), funs(as.numeric(as.character(.))))
 
#calculate each question's mean
post_week5_means <- post_week5 %>% 
  summarise_each(funs(mean( .,na.rm = TRUE)))

#rename average row
post_week5_means$Q1[is.na(post_week5_means$Q1)] <- "Average"

#append means to original scores
post_week5_with_means <- rbind(post_week5, post_week5_means)

print(post_week5_with_means)
```

#Post-Test: Self & Cultural Authenticity

QID12_

```{r pre}
pre <- pre_survey_clean %>% 
  select(
    Q1, 
    starts_with("QID12_")
  ) %>% 
  #keep only numeric values
  mutate(across(starts_with(c("QID12_")), ~ gsub("[^0-9.-]+", "", .))) %>%
  #change class to numeric for all columns that start with "Q9_"
  mutate_at(vars(starts_with("QID12_")), funs(as.numeric(as.character(.))))
 
#calculate each question's mean
pre_means <- pre %>% 
  summarise_each(funs(mean( .,na.rm = TRUE)))

#rename average row
pre_means$Q1[is.na(pre_means$Q1)] <- "Average"

#append means to original scores
pre_with_means <- rbind(pre, pre_means)

print(pre_with_means)
```

```{r post}
post <- post_survey_clean %>% 
  select(
    Q1, 
    starts_with("QID12_")
  ) %>% 
  #keep only numeric values
  mutate(across(starts_with(c("QID12_")), ~ gsub("[^0-9.-]+", "", .))) %>%
  #change class to numeric for all columns that start with "Q9_"
  mutate_at(vars(starts_with("QID12_")), funs(as.numeric(as.character(.))))
 
#calculate each question's mean
post_means <- post %>% 
  summarise_each(funs(mean( .,na.rm = TRUE)))

#rename average row
post_means$Q1[is.na(post_means$Q1)] <- "Average"

#append means to original scores
post_with_means <- rbind(post, post_means)

print(post_with_means)
```

##Item 4

Pre: QID12_4
Week 4: QID12_4

```{r}
#pre results
pre_item <- pre_with_means %>% 
  select(Q1,
         QID12_4) %>% 
  rename(PreSurvey = QID12_4)

print(pre_item)

#week 2 (AKA post) results
post_item <- post_with_means %>% 
  select(Q1,
         QID12_4) %>% 
  rename(PostTest = QID12_4)

print(post_item)

#combine pre and post results
item <- full_join(x = pre_item, y = post_item) %>% 
  rename(Participant = Q1)
print(item)
```

##Item 8

Pre: QID12_8
Week 4: QID12_8

```{r}
#pre results
pre_item <- pre_with_means %>% 
  select(Q1,
         QID12_8) %>% 
  rename(PreSurvey = QID12_8)

print(pre_item)

#week 2 (AKA post) results
post_item <- post_with_means %>% 
  select(Q1,
         QID12_8) %>% 
  rename(PostTest = QID12_8)

print(post_item)

#combine pre and post results
item <- full_join(x = pre_item, y = post_item) %>% 
  rename(Participant = Q1)
print(item)
```

##Item 10

Pre: QID12_10
Week 4: QID12_10

```{r}
#pre results
pre_item <- pre_with_means %>% 
  select(Q1,
         QID12_10) %>% 
  rename(PreSurvey = QID12_10)

print(pre_item)

#week 2 (AKA post) results
post_item <- post_with_means %>% 
  select(Q1,
         QID12_10) %>% 
  rename(PostTest = QID12_10)

print(post_item)

#combine pre and post results
item <- full_join(x = pre_item, y = post_item) %>% 
  rename(Participant = Q1)
print(item)
```

##Item 12

Pre: QID12_12
Week 4: QID12_12

```{r}
#pre results
pre_item <- pre_with_means %>% 
  select(Q1,
         QID12_12) %>% 
  rename(PreSurvey = QID12_12)

print(pre_item)

#week 2 (AKA post) results
post_item <- post_with_means %>% 
  select(Q1,
         QID12_12) %>% 
  rename(PostTest = QID12_12)

print(post_item)

#combine pre and post results
item <- full_join(x = pre_item, y = post_item) %>% 
  rename(Participant = Q1)
print(item)
```

##Item 14

Pre: QID12_14
Week 4: QID12_14

```{r}
#pre results
pre_item <- pre_with_means %>% 
  select(Q1,
         QID12_14) %>% 
  rename(PreSurvey = QID12_14)

print(pre_item)

#week 2 (AKA post) results
post_item <- post_with_means %>% 
  select(Q1,
         QID12_14) %>% 
  rename(PostTest = QID12_14)

print(post_item)

#combine pre and post results
item <- full_join(x = pre_item, y = post_item) %>% 
  rename(Participant = Q1)
print(item)
```

##Item 16

Pre: QID12_16
Week 4: QID12_16

```{r}
#pre results
pre_item <- pre_with_means %>% 
  select(Q1,
         QID12_16) %>% 
  rename(PreSurvey = QID12_16)

print(pre_item)

#week 2 (AKA post) results
post_item <- post_with_means %>% 
  select(Q1,
         QID12_16) %>% 
  rename(PostTest = QID12_16)

print(post_item)

#combine pre and post results
item <- full_join(x = pre_item, y = post_item) %>% 
  rename(Participant = Q1)
print(item)
```



